### 2017-01-16 paper/intro.tex
pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is important.

Several approaches have been proposed in the literature to address the
regression testing problem, with the focus mainly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing testing workloads.  Evidence of this are the
Google TAP system~\cite{google-tap,google-ci} and Microsoft's
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficienctly build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building
proprietary infrastructures for running tests is a legitimate approach
to mitigate the regression testing problem.  However, for projects
with low budgets and yet relatively heavy testing workloads, this
solution may not be economically viable.  This paper focuses on the
problem of understanding how critical the regression testing problem
is in open-source projects.  To the best of our knowledge no prior
work investigated this problem, which is becoming more important given
the tremendous popularity of open-source development.

@@

\Fix{---------------- parei aqui...}

More precisely, we studied (1) how prevalent long-running test suites
are in open-source software projects.  To that end, we selected from
\github{} \numSubjs{} highly-popular Java projects containing Maven
build files.  (Section~\ref{sec:eval} details our selection
methodology.)  To run this experiment we used the default Maven
configuration to run a project's test suite and a 16GB memory i7-4790
Intel processor machine, which we carefully isolated.  Our results
indicate that the test suite of nearly one in every five projects from
our set (\percentMedLongRunning) takes at least 5m to run.  On
average, one of those test suites take \averageMedLongRunning{} to
run.  These results suggest that open-source projects often contain
long running test suites.

\Mar{missing connection. why
  parallelism?}  From this result we investigated (2) how frequently
the projects we considered use parallelization to speedup test runs.
Our results indicate that \percentParallelForLongRunning{} of
long-running test suites do use parallelism to speedup execution.
Given the popularity of this solution, we further studied: (3) what
are the causes of high execution cost in individual tests (CPU vs. IO)
and (4) how uniformly cost is distributed across tests.  These
questions help to assess the impact of parallelization in test suite
execution.  Intuitively, IO-intensive test suites and test suites with
uneven distribution of cost per test are factors that limit the
benefits of parallelization.  Results indicate that \Fix{...}
Finally, we investigated (5) what are the limitations related to
parallelization that could justify adoption resistance.

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite.  Dealing with high testing
costs is an important problem in software engineering research and
practice (as to reduce late test failure reports).

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workloads.  Evidence of this are
the Google TAP system~\cite{google-tap,google-ci} and Microsoft's
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficienctly build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  This paper reports on a study we
conducted analyzing three orthogonal dimensions of regression testing
in open-source projects.  We argue that this an important problem
given the tremendous popularity of open-source development and
regression testing research.  The dimensions of analysis are as
follows.

\begin{itemize}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Impact (and issues) of parallelization.}  
\end{itemize}

@@

%% RQ1 + RQ2
To assess how prevalent long-running test suites are in open-source
projects, we selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven}.  (Section~\ref{sec:eval}
details our selection methodology.)  To run each test suite, we used a
16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
eight virtual CPUs (four cores with two native threads each) and the
default Maven configuration of each project.  Our results indicate
that \percentMedLongRunning{} of the test suites take at least 1m to
run and nearly 8\% of the test suites take more than 5m to run.
Including medium and long-running test suites ($>$1m), a test suite
takes \averageMedLongRunning{} to run, on average.  These results
indicate that open-source projects often contain long running test
suites.  Furthermore, we found that although \Fix{...time
  distribution...}

\Mar{missing connection. why parallelism?}  From these results we
investigated (2) how frequently the projects we considered use
parallelization to speedup test runs.  Our results indicate that
\percentParallelForLongRunning{} of long-running test suites do use
parallelism to speedup execution.  Given the popularity of this
solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the benefits of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related to parallelization that could justify adoption
resistance.
